Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-06-09 bbbq_article.tex
Do stuff on Peregrine (create data) and on local (create figures)
stub 'ic50s_per_haplotype' result

\begin{table}[!htbp]
  \input{ep_vs_mhcn/ep_vs_mhcn.latex}
  \caption{
    Correlation coefficients for different haplotypes
    \richel{Used randomly simulated polypeptides, results are real}
  }
  \label{table:ep_vs_mhcn}
\end{table}

>>>>

%\begin{table}[!htbp]
%  \input{ep_vs_mhcn/ep_vs_mhcn.latex}
%  \caption{
%    Correlation coefficients for different haplotypes
%    \richel{Used randomly simulated polypeptides, results are real}
%  }
%  \label{table:ep_vs_mhcn}
%\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{IC50s per haplotype}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Here we have simulated \richel{some, say 100} random peptides.
Per peptide, we measured the IC50 
per MHC-I (figure \label{fig:ic50s_per_haplotype_mhc_1})
and MHC-II  (figure \label{fig:ic50s_per_haplotype_mhc_2}) haplotype.

\begin{figure}[!htbp]
  \includegraphics[width=0.9\textwidth]{ic50s_per_haplotype/ic50s_per_haplotype_mhc_1.png}
  Predicted IC50s (in nM) per MHC-I haplotype
  \caption{
    \richel{Used randomly simulated polypeptides, results are real}
  }
  \label{fig:ic50s_per_haplotype_mhc_1}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=0.9\textwidth]{ic50s_per_haplotype/ic50s_per_haplotype_mhc_2.png}
  Predicted IC50s (in nM) per MHC-II haplotype
  \caption{
    \richel{Used randomly simulated polypeptides, results are real}
  }
  \label{fig:ic50s_per_haplotype_mhc_2}
\end{figure}
